Simulating ordinal data

### 2024-01-30 submission/cover-letter/cover-letter.Rmd
updating

We wish to submit our work "*`r rmarkdown::metadata$paper`*" for consideration by `r rmarkdown::metadata$journal` (special issue "Tutorials on Quantitative Methods"). Ordinal data are very common in any area of Psychology from social psychology, to clinical assessment and also experimental psychology. Several authors suggested that ordinal data requires appropriate descriptive statistics and modeling methods but very often researchers ignore the ordinal nature of the variable using standard statistical techniques e.g., linear regressions. This approach can introduce inferential errors, biased estimates, and wrong predictions.

>>>>

We wish to submit our full manuscript "*`r rmarkdown::metadata$paper`*" for consideration by `r rmarkdown::metadata$journal` (special issue "Tutorials on Quantitative Methods"). Ordinal data are very common in any area of Psychology from social psychology, to clinical assessment and also experimental psychology. Several authors suggested that ordinal data requires appropriate descriptive statistics and modeling methods but very often researchers ignore the ordinal nature of the variable using standard statistical techniques e.g., linear regressions. This approach can introduce inferential errors, biased estimates, and wrong predictions.
